Article template&#58; A reproducible RMarkdown template for Elsevier's journal format with examples for beginners

### 2019-02-12 Paper/Manuscript.Rmd
Edits to yaml - Latex caption package is reqired for plots with gt

---
title: An R markdown template for Elsevier journals with examples for beginners 
author:
  - name: Paul Raftery 
    email: p.raftery@berkeley.edu
    affiliation: CBE
    footnote: Corresponding Author
  - name: Next contributor 
    affiliation: Organisation2
address:
  - code: CBE
    address: Center for the Built Environment, UC Berkeley, 390 Wurster Hall, Berkeley, CA, 94720, USA
  - code: Organisation2
    address: Another organization, and their address

abstract: Enter the text for your abstract here
journal: "Building and Environment"
date: "`r Sys.Date()`"
bibliography: Bibliography.bib
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
csl: elsevier-with-titles.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
header-includes:
- \usepackage{setspace}
- \doublespacing
---

>>>>

---
title: Article template&#58; A reproducible RMarkdown template for Elsevier's journal format with examples for beginners  
author:
  - name: Paul Raftery 
    email: p.raftery@berkeley.edu
    affiliation: CBE
    footnote: Corresponding Author
  - name: Dana Miller
    affiliation: CBE
  - name: Next contributor
    affiliation: Organization2
address:
  - code: CBE
    address: Center for the Built Environment, UC Berkeley, 390 Wurster Hall, Berkeley, CA, 94720, USA
  - code: Organisation2
    address: Another organization, and their address

abstract: Enter the text for your abstract here. All data and analysis code in this template is publicly available at [https://github.com/CenterForTheBuiltEnvironment/rmd-example](https://github.com/CenterForTheBuiltEnvironment/rmd-example) and can be freely adapted and reused. Suggestions or pull requests to improve this template or create additional templates are welcome.

journal: "Building and Environment"
date: "`r Sys.Date()`"
bibliography: Bibliography.bib
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
csl: elsevier-with-titles.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{caption}
---
